\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage{bm}
\begin{document}
Notation:
\begin{itemize}
\item A lineup with $m$ panels
\item Evaluated $K$ times
\item With panel selection counts $\bm c = (c_1, ..., c_m)$, so $K = \sum_{i=1}^m c_i$
\item Each panel is selected with probability $\bm\theta = (\theta_1, ..., \theta_m)$
\end{itemize}

We model $\bm c \sim \text{Multinomial}(\bm\theta)$, that is, 
$$p(\bm c | \bm \theta) = \frac{K!}{\prod_{i=1}^m c_i!} \prod_{i=1}^m \theta_i^{c_i}$$

We model $\bm \theta  \sim \text{Beta}(\bm \alpha)$, that is, 
$$p(\bm \theta) \sim \frac{1}{B(\bm \alpha)} \prod_{i=1}^m\theta_i^{\alpha_i - 1}$$

As $p(\bm\theta)$ is a prior distribution, we might instead write it as $\pi(\bm\theta)$ or even $\pi(\bm\theta|\bm\alpha)$ to emphasize the addition of the hyperparameter $\bm\alpha$. $\bm\alpha = (\alpha_1, ..., \alpha_m)$ is the concentration hyperparameter for our Beta prior. 

For Bayesian inference, we would typically be interested in $\bm\theta$. In this case we stop short of calculating $p(\bm\theta|\bm c)$ because we don't actually care about $\bm\theta$ - we're less interested in the panel selection probabilities than we are in adding additional flexibility to our model by including a hyperparameter. Thus, we're much closer to a mixture model than to actual Bayesian inference here, even if I did start out using full-on Bayes. 

Just as an explanation of how Bayesian inference would work...

Basic Bayes' theorem says $P(A|B) = \displaystyle\frac{P(B|A)P(A)}{P(B)}$. So in this case, we would write 
\begin{align*}
p(\bm\theta | \bm c) &= \frac{p(\bm c|\bm\theta)p(\bm \theta)}{\int p(\bm c|\bm \theta)p(\bm\theta) d\bm\theta}\\
&\propto \left(\frac{\left(\sum_{i=1}^m c_i\right)!}{\prod_{i=1}^m c_i!}\prod_{i=1}^m\theta_i^{c_i}\right)\left(\frac{1}{B(\bm\alpha)}\prod_{i=1}^m\theta_i^{\alpha_i - 1}\right)
\end{align*}
Where the normalizing constant A is defined such that $$\frac{1}{A} = \displaystyle\int\left(\frac{\left(\sum_{i=1}^m c_i\right)!}{\prod_{i=1}^m c_i!}\prod_{i=1}^m\theta_i^{c_i}\right)\left(\frac{1}{B(\bm\alpha)}\prod_{i=1}^m\theta_i^{\alpha_i - 1}\right)d\bm\theta $$

\begin{align*}
p(\bm\theta | \bm c) &\propto \left(\frac{\left(\sum_{i=1}^m c_i\right)!}{\prod_{i=1}^m c_i!}\prod_{i=1}^m\theta_i^{c_i}\right)\left(\frac{1}{B(\bm\alpha)}\prod_{i=1}^m\theta_i^{\alpha_i - 1}\right) \\
&\propto\underbrace{ \left(\frac{\left(\sum_{i=1}^m c_i\right)!}{\prod_{i=1}^m c_i!}\frac{1}{B(\bm\alpha)}\right)}_{\text{Constant with respect to }\bm\theta}\prod_{i=1}^m \theta_i^{c_i + \alpha_i - 1}\\
&\propto \prod_{i=1}^m \theta_i^{c_i + \alpha_i - 1} 
\end{align*}

Where now the normalizing constant is $\tilde A = A \cdot \left(\frac{\left(\sum_{i=1}^m c_i\right)!}{\prod_{i=1}^m c_i!}\frac{1}{B(\bm\alpha)}\right)$

But, since we only care about $\bm c$ and $\bm \alpha$, we would just want to integrate out $\bm\theta$ anyways (which is, conveniently, what we have to do to calculate that normalizing constant). 

So, using $\bm x$ to represent a specific set of observed panel selection counts, where $\bm c$ represents the random variable, we use the law of total probability

\begin{align*}
\frac{1}{A} = p(\bm c) & = \int p(\bm c | \bm\theta) p(\bm\theta) d\bm\theta\\
&=\left(\frac{\left(\sum_{i=1}^m c_i\right)!}{\prod_{i=1}^m c_i!}\frac{1}{B(\bm\alpha)}\right) \underbrace{\int \prod_{i=1}^m \theta_i^{c_i + \alpha_i - 1}d\bm\theta}_{\text{Beta distribution, integrates to }B(\bm\alpha + \bm c)}\\
&= \frac{\left(\sum_{i=1}^m c_i\right)!}{\prod_{i=1}^m c_i!}\frac{B(\bm\alpha + \bm c)}{B(\bm\alpha)}
\end{align*}

For the sake of completeness, our normalizing constant for $p(\bm\theta | \bm c)$ is $$\tilde A = \frac{\frac{\left(\sum_{i=1}^m c_i\right)!}{\prod_{i=1}^m c_i!}\frac{1}{B(\bm\alpha)}}{\frac{\left(\sum_{i=1}^m c_i\right)!}{\prod_{i=1}^m c_i!}\frac{B(\bm\alpha + \bm c)}{B(\bm\alpha)}} = \frac{1}{B(\bm \alpha + \bm c)},$$
which means that $$p(\bm\theta | \bm c) = \frac{1}{B(\bm \alpha + \bm c)} \prod_{i=1}^m \theta_i^{c_i + \alpha_i - 1}$$
or, in other words, the posterior distribution for $\bm\theta$ is $\text{Beta}(\bm\alpha + \bm c)$




\end{document}